Appendix

### 2014-11-26 Rmarkdown/appendix.Rmd
Typo in R code

```{r dinucleotide_distribution, fig.lp = "fig:dinuclotide_distribution"}
library(ggplot2)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)
edf <- nf %*% t(nf) / (sum(nf %*% t(nf))) * 100
x <- data.frame(Dinucleotide = names(rowSums(df)),
                Observed = as.vector(100 * rowSums(df) / sum(as.numeric(df))), 
                Expected = as.vector(edf))
ggplot(x, aes(x = Dinucleotide, y = Observed / Expected)) + 
  geom_point(size = 5) + coord_cartestian(ylim = c(0, 1.5)) + 
  ggtitle("CpGs are underrepresented in human reference genome (hg19)") + 
  thesis_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept = 1, linetype = 2)
```

>>>>

```{r dinucleotide_distribution, fig.lp = "fig:dinuclotide_distribution"}
library(ggplot2)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)
edf <- nf %*% t(nf) / (sum(nf %*% t(nf))) * 100
x <- data.frame(Dinucleotide = names(rowSums(df)),
                Observed = as.vector(100 * rowSums(df) / sum(as.numeric(df))), 
                Expected = as.vector(edf))
ggplot(x, aes(x = Dinucleotide, y = Observed / Expected)) + 
  geom_point(size = 5) + coord_cartesian(ylim = c(0, 1.5)) + 
  ggtitle("CpGs are underrepresented in human reference genome (hg19)") + 
  thesis_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept = 1, linetype = 2)
```
